Scattering of massless particles: scalars, gluons and gravitons

### 2024-07-05 test/main.tex
New

\documentclass{beamer}
\usetheme{Madrid}
\usefonttheme{professionalfonts}
\usepackage{tikz}
\usepackage{svg}
\AtBeginSection[]{
\begin{frame} 
    \frametitle{Contents}
    \tableofcontents[currentsection]
\end{frame}
}
\title[CHY formula]{Scattering of massless particles: scalars, gluons and gravitons}
\subtitle{Freddy Cachazo, Song He, Ellis Ye Yuan}
\author{Su Yingze}
\institute{Nagoya University}
\date[7 23rd 2024]{July 23rd 2024} 
\begin{document}
\frame{\titlepage}

\section{Why the S-matrix is so important?}
\begin{frame}
    It is well known that in the conventional quantum field theory, S-matrix is a deduced physical quantity following
    unitarity and localty. But as the understanding of scatering amplitudes improves, by using the amplituhedron method,
    S-matrix can be constructed directly from a special kind of geometry object and we even have no need to introduce the Lagrangian
    of the specific theory. Also the localty and unitarity can be the outcome from the request of positivity instead of input or previous constraints.
    It may give us some implications about the significance of S-matrix and encourage us to reconstruct the field theory in another way.
\end{frame}
\begin{frame}{}
    \begin{itemize}
        \item BCFW recursion relation.
        \begin{equation*}
            \!\!\!\!A_n ~= \!\!\!\!\sum_{\text{diagrams}~I} \hat{A}_\text{L}(z_I) 
            \,\frac{1}{P_I^2}\,
            \hat{A}_\text{R}(z_I)
               ~~=
               \!\!\!\!\sum_{\text{diagrams}~I}
           \raisebox{-5.5mm}{\includegraphics[height=1.4cm]{recrel1.pdf}}
           \,.
        \end{equation*}
        \item Dual superconformal symmetry of $\mathcal{N}=4$ Super Yang-Mills amplitude.
        \item Generalized unitarity
        \item Positive geometry and Amplituhedra.
        \item \dots
    \end{itemize}
    \begin{figure}
        \centering
        \includegraphics[width=0.8\linewidth]{Grassmanian-Image.jpg}
    \end{figure}
\end{frame}
\section{Review of some pertinent results}
\begin{frame}{Gauge theory color structure}
    At tree level, with particles in the adjoint representaion of gauge group SU(N), the amplitude can be 
decomposed as
\textcolor{red}{\begin{equation*}
    \mathcal{A}_n^{tree}(1,2,3,\dots,n)=\sum _{\mathcal{P}(2,3,\dots,n)}Tr[T^{a_1}T^{a_2}T^{a_3}\dots
    T^{a_n}]A_n^{tree}[1,2,3,\dots,n]
\end{equation*}}

here we ommit the coupling constant g, and $A_n^{tree}$ is called tree-level color-ordered partial amplitude.
Notice that this basis includes \textcolor{red}{$(n-1)!$} independent amplitudes.
\end{frame}
\begin{frame}
    Color-ordered partial amplitudes satisfy a set of well-known properties,
    \begin{itemize}
        \item Cyclic:\quad $$A_n^{tree}[1,2,3,\dots,n]=A_n^{tree}[2,3,\dots,n,1]$$
        \item Reflection: \quad $$A_n^{tree}[1,2,3,\dots,n]=(-1)^nA_n^{tree}[n,\dots,3,2,1]$$
        \item "photon" decoupling: \quad $$\sum_{\sigma\in \text{cyclic}}A_n^{tree}[1,\sigma(2,3,\dots,n)]=0$$
        \item KK(Kleiss-Kuijf) relation:\quad $$A_n^{tree}[1,{\alpha},n,{\beta}]=(-1)^{n_\beta}
        \sum_{\left\{\sigma\right\}_i\in OP(\left\{\alpha\right\},\left\{\beta\right\}^T)}A_n^{tree}[1,\left\{\sigma\right\}_i,n]$$
    \end{itemize}
    where the OP means ordered permutaions, that is all permutations of$\left\{\alpha\right\},\left\{\beta\right\}^T$
    that matains the order of individual elements of each set.
\end{frame}
\begin{frame}
    For example, a five point amplitude $A_n^{tree}(1,\{2,3\},5,\{4\})$, we have
\begin{equation*}
    A_n^{tree}[1,2,3,5,4]=-A_n^{tree}[1,2,3,4,5]-A_n^{tree}[1,2,4,3,5]-A_n^{tree}[1,4,2,3,5]
\end{equation*}
The other five point relations can be obtained by permuting legs 2,3,4 and using cyclic and reflection properties.
\\ \hspace*{\fill}\\
This means that the six amplitudes $A_n^{tree}(1,\mathcal{P}\{2,3,4 \},5 )$ form a basis of remaining five-point partial amplitudes.
\textcolor{red}{More generally, for multiplicity n, the KK relation can be used to rewrite any color-ordered partial amplitude in terms of only $(n-2)!$
basis partial amplitudes, where two legs are fixed(usually choose 1 and n).}
\end{frame}
\begin{frame}{A Similar Structure}
    It can be proved that tree level amplitudes can also be decomposed like 
\begin{equation*}
    \mathcal{A}_n^\text{tree}=\sum_{\sigma\in S_{n-2}}\tilde{f}^{a_1a_{\sigma_1}b_1}\tilde{f}^{b_1a_{\sigma_2}b_2}\cdots\tilde{f}^{b_{n-3}a_{\sigma_{n-2}}a_n}\tilde{A}_n(1,\sigma_1,\sigma_2,\ldots,\sigma_{n-2},n)
\end{equation*}
The basis is called DDM and more convenient in parctice. It is easy to realize that the number of basis amplitudes is also \textcolor{red}{$(n-2)!$} with fiexed particle labels 1 and n.
\end{frame}
\begin{frame}
    \begin{Large}
        \textcolor{red}{How can we realize the existence of this basis?}
    \end{Large}
\\ \hspace*{\fill}\\
We just need to notice the contribution from ladder diagram
\begin{figure}[htb]
    \centering
    \includegraphics[width=1\linewidth]{1.png}
\end{figure}
And any (three vertex) diagram, by using the Jacobbi identity like 
\begin{figure}[htb]
    \centering
    \includegraphics[width=1\linewidth]{2.png}
\end{figure}
can be transformed to the ladder diagram. It has been proved that $\textcolor{red}{\tilde{A}_n(\dots)}$ here is identical to $\textcolor{red}{A_n^{tree}[\dots]}$ in the trace basis.
\end{frame}
\begin{frame}{Color-Kinematics Duality and BCJ Relation}
The Color-Kinematics Duality here is not the complete version, but we can sketch some point from lower point case
\end{frame}

@@

    To discribe the n-punctured sphere more properly, we can introduce the Riemann sphere as
    \begin{equation*}
        \mathbb{CP}^1\cong \mathcal{S}^2\cong \mathbb{C}\cup\{\infty\}
    \end{equation*}
    and n-punctured Riemann sphere can be discribed by $SL(2,\mathbb{C})$ affine coordinates ${\sigma_1,\sigma_2,\ldots,\sigma_n}$, that is to say we have a equvilance relation
    \begin{align*}
        \{\sigma_1,\sigma_2,\ldots,\sigma_n\}\sim\{\psi(\sigma_1),\psi(\sigma_2),\ldots,\psi(\sigma_n)\},\\\psi(\sigma):=\frac{\alpha\sigma+\beta}{\gamma\sigma+\delta},\quad\alpha,\beta,\gamma,\delta\in\mathbb{C},\alpha\delta-\beta\gamma=1
    \end{align*}
    because of the redundancy of 
\end{frame}
\begin{frame}
    From this map, we can easily obtain the main ingredients of this report \\

    \begin{block}{\textcolor{red}{Scattering equations}}
        \begin{equation*}
            \sum_{b\neq a } \frac{s_{ab}}{\sigma_a-\sigma_{b}}=0,\qquad a\in \{1,\dots,n\}
        \end{equation*}
    \end{block}
    It has been proved that the number of solutions in any dimension is $\alert{(n-3)!}$, and only \alert{n-3} of the equtions are independent, so we can rewrite the scattering equations as following 
    \begin{equation*}
        \sum_{b\neq a } \frac{s_{ab}}{\sigma_a-\sigma_{b}}=0,\quad a\in \{4,5,\dots,n\}\quad and\quad  \sigma_1\rightarrow\infty,\sigma_2=0,\sigma_3=1
    \end{equation*}
\end{frame}
\begin{frame}{KLT Relation}
    So-called KLT relation, in the language of field theory, refers to the decomposition of \alert{gravity amplitudes} to \alert{two gauge theory amplitues}. 
    \begin{table}[]
        \resizebox{\textwidth}{!}{
        \begin{tabular}{|l|l|l|l|l|}
        \hline
         \(\mathcal{N}\) & Factors & Supergravity   \\ \hline
         8 &   \(\mathcal{N}=4SYM\otimes \mathcal{N}=4SYM\)      &   pure \(\mathcal{N}=8 \)SG             \\ \hline
         6 &   \(\mathcal{N}=4SYM\otimes \mathcal{N}=2SYM\)      &   pure \(\mathcal{N}=6 \)SG             \\ \hline
         5 &   \(\mathcal{N}=4SYM\otimes \mathcal{N}=1SYM\)      &   pure \(\mathcal{N}=5 \)SG             \\ \hline
         4 &   \(\mathcal{N}=4SYM\otimes (\mathcal{N}=0YM+n_\nu scalars)\)      &    \(\mathcal{N}=4 \)SG,\(n_\nu\)vector multiplets             \\ \hline
         4 &   \(\mathcal{N}=2SYM\otimes \mathcal{N}=2SYM\)      &    \(\mathcal{N}=4 \)SG,2 vector multiplets            \\ \hline
         3 &   \(\mathcal{N}=2SYM\otimes \mathcal{N}=1SYM\)      &    \(\mathcal{N}=3 \)SG,1 vector multiplet           \\ \hline
         2 &   \(\mathcal{N}=2SYM\otimes (\mathcal{N}=0YM+n_\nu scalars)\)      &    \(\mathcal{N}=2 \)SG,\(n_\nu\) multiplets+1 vector multiplets            \\ \hline
         2 &   \(\mathcal{N}=1SYM\otimes \mathcal{N}=1SYM\)       &    \(\mathcal{N}=2 \)SG ,1 hypermultiplet               \\ \hline
         1 &   \(\mathcal{N}=1SYM\otimes (\mathcal{N}=0YM+n_\nu scalars)\)      &     \(\mathcal{N}=1 \)SG,  \(n_\nu\) vector and 1 chiral multiplet           \\ \hline
        \end{tabular}
        }
        \end{table}
\end{frame}
\begin{frame}{KLT Orthogonality}
    $\bullet$ KLT orthogonality is a striking property of the solutions to scattering equations.
    \begin{block}{Proposition 1}
        \begin{equation*}
            \frac{(i,j)}{(i,i)^{\frac12}(j,j)^{\frac12}}=\delta_{ij}
        \end{equation*}
    \end{block}

@@

    It is worth to computed the measure explictly.Aftering "gauge fixing" the $SL(2,\mathbb{C})$ redundancy, one finds 

@@

\end{frame}
\begin{frame}
    Likewise the decomposition in the first section, it is more usually to write the amplitudes in terms of colore basis
    \begin{equation*}
        \boxed{\mathbf{c}_\alpha\equiv\sum_{\mathsf{c}_1,...,\mathsf{c}_{n-3}}f_{\mathsf{a}_1\mathsf{a}_{\alpha(2)}\mathsf{c}_1}\cdots f_{\mathsf{c}_{n-3}\mathsf{a}_{\alpha(n-1)}\mathsf{a}_n}}
    \end{equation*}
    where $\alpha \in S_{n-2}$. The amplitude is 
    \begin{equation*}
        \mathcal{M}_n^{(0)}=\sum_{\alpha,\beta\in S_{n-2}}\mathbf{c_\alpha}\tilde{\mathbf{c_\beta}}m_{n}^{(0)}(\alpha|\beta)
    \end{equation*}
\end{frame}
\begin{frame}
    \frametitle{Examples}
    \begin{itemize}
        \item The simplest example is the 3 point case
        \begin{equation*}
            \mathcal{M}_3^{(0)}(1^{aa^\prime,bb^\prime,cc^\prime})=(\sigma_{12}\sigma_{23}\sigma_{31})^2\frac{f_{abc}f_{a^\prime b^\prime c^\prime}}{(\sigma_{12}\sigma_{23}\sigma_{31})^2}=f_{abc}f_{a^\prime b^\prime c^\prime}
        \end{equation*}
        It actually gives the correct answer.
        \item The 4 point case is a little complex. Solving the scattering equations with $\sigma_1=0,\sigma_2=1,\sigma_3=\infty$ gives $\sigma_4=-s_{23}/s_{12}$. Define
        $s_{12}=s$, $s_{23}=t$, $s_{13}=u$, the color factors are 
        \begin{equation*}
            \mathbf{c_s}=\sum_bf_{a_1a_2b}f_{ba_3a_4},\mathbf{c_t}=\sum_bf_{a_1a_4b}f_{ba_3a_2},\mathbf{c_u}=\sum_bf_{a_1a_3b}f_{ba_2a_4}
        \end{equation*}
        Denoting the ordering $(1324)$ as $P$ and comuputing $\det{'}\Phi=\frac{s^2}{t}/(\sigma_{12}\sigma_{23}^2\sigma_{31}\sigma_{34}\sigma_{42})$, one gets
    \end{itemize}
\end{frame}
\begin{frame}
    \begin{align*}
        \!\!\!\!\mathcal{M}_4^{(0)}&=\mathbf{c_s}\tilde{\mathbf{c_s}}m_4^{(0)}(I;I)+\mathbf{c_s}\tilde{\mathbf{c_u}}m_4^{(0)}(I;P)+\mathbf{c_u}\tilde{\mathbf{c_s}}m_4^{(0)}(P;I)+\mathbf{c_u}\tilde{\mathbf{c_u}}m_4^{(0)}(P;P)\\
        &=\mathbf{c_s}\tilde{\mathbf{c_s}}\frac{u}{st}+(\mathbf{c_s}\tilde{\mathbf{c_u}}+\mathbf{c_u}\tilde{\mathbf{c_s}})\frac{1}{t}+\mathbf{c_u}\tilde{\mathbf{c_u}}\frac{s}{ut}\\
        &=-\frac{\mathbf{c_s}\tilde{\mathbf{c_s}}}{s}-\frac{\mathbf{c_t}\tilde{\mathbf{c_t}}}{t}-\frac{\mathbf{c_u}\tilde{\mathbf{c_u}}}{u}
    \end{align*}
    \quad \quad as expected for a color-dressed cubic theory.
    \begin{itemize}
        \item For the five point, I just give the results of some double partial amplitudes.
        Denoting the orderings as $I=P_0$, $(13245)=P_1$, $(12435)=P_2$, $(14325)=P_3$, $(13425)=P_4$, $(14235)=P_5$
        \begin{equation*}
            \begin{aligned}&m_5^{(0)}(I|I)=\frac{1}{s_{12}s_{34}}+\frac{1}{s_{23}s_{45}}+\frac{1}{s_{34}s_{51}}+\frac{1}{s_{45}s_{12}}+\frac{1}{s_{51}s_{23}},\\&m_5^{(0)}(I|P_1)=-\frac{1}{s_{23}}\left(\frac{1}{s_{45}}+\frac{1}{s_{12}}\right),\quad
                m_5^{(0)}(I|P_2)=-\frac{1}{s_{34}}\left(\frac{1}{s_{51}}+\frac{1}{s_{12}}\right).\end{aligned}
        \end{equation*}
    \end{itemize}
\end{frame}
\begin{frame}
    \begin{align*}
        &m_5^{(0)}(I|P_3)=-\frac{1}{s_{51}}\left(\frac{1}{s_{23}}+\frac{1}{s_{34}}\right),\quad  m_5^{(0)}(I|P_4)=-\frac{1}{s_{34}s_{51}},\\
        &m_5^{(0)}(I|P_5)=0
    \end{align*}
    From there examples, it is easy to see that when both permutations in $m_n^{(0)}(\alpha|\beta)$ are the same, then the answer is a sum over all color-orded
    trivalent diagrams; When the two permutations are different, it gives a subset of terms of $m_n^{(0)}(\alpha|\alpha)$. 
    \\ \hspace*{\fill}\\
    More explictly,

>>>>

\documentclass{beamer}
\usetheme{Madrid}
\usefonttheme{professionalfonts}
\usepackage{tikz}
\usepackage{svg}
\usepackage{graphics}
\AtBeginSection[]{
\begin{frame} 
    \frametitle{Contents}
    \tableofcontents[currentsection]
\end{frame}
}
\title[CHY formula]{Scattering of massless particles: scalars, gluons and gravitons}
\subtitle{Freddy Cachazo, Song He, Ellis Ye Yuan}
\author{Su Yingze}
\institute{Nagoya University}
\date[7 23rd 2024]{July 23rd 2024} 
\begin{document}
\frame{\titlepage}

\section{Why the S-matrix is so important?}
\begin{frame}
    It is well known that in the conventional quantum field theory, S-matrix is a deduced physical quantity following
    unitarity and localty. But as the understanding of scatering amplitudes improves, by using the amplituhedron method,
    S-matrix can be constructed directly from a special kind of geometry object and we even have no need to introduce the Lagrangian
    of the specific theory. Also the localty and unitarity can be the outcome from the request of positivity instead of input or previous constraints.
    It may give us some implications about the significance of S-matrix and encourage us to reconstruct the field theory in another way.
\end{frame}
\begin{frame}{}
    \begin{itemize}
        \item BCFW recursion relation.
        \begin{equation*}
            \!\!\!\!A_n ~= \!\!\!\!\sum_{\text{diagrams}~I} \hat{A}_\text{L}(z_I) 
            \,\frac{1}{P_I^2}\,
            \hat{A}_\text{R}(z_I)
               ~~=
               \!\!\!\!\sum_{\text{diagrams}~I}
           \raisebox{-5.5mm}{\includegraphics[height=1.4cm]{recrel1.pdf}}
           \,.
        \end{equation*}
        \item Dual superconformal symmetry of $\mathcal{N}=4$ Super Yang-Mills amplitude.
        \item Generalized unitarity
        \item Positive geometry and Amplituhedra.
        \item \dots
    \end{itemize}
    \begin{figure}
        \centering
        \caption{Positive geometry}
        \includegraphics[width=0.4\linewidth]{Grassmanian-Image.jpg}
    \end{figure}
\end{frame}
\section{Review of some pertinent results}
\begin{frame}{Gauge theory color structure}
    At tree level, with particles in the adjoint representaion of gauge group SU(N), the amplitude can be 
decomposed as
\textcolor{red}{\begin{equation*}
    \mathcal{A}_n^{tree}(1,2,3,\dots,n)=\sum _{\mathcal{P}(2,3,\dots,n)}Tr[T^{a_1}T^{a_2}T^{a_3}\dots
    T^{a_n}]A_n^{tree}[1,2,3,\dots,n]
\end{equation*}}

here we ommit the coupling constant g, and $A_n^{tree}$ is called tree-level color-ordered partial amplitude.
Notice that this basis includes \textcolor{red}{$(n-1)!$} independent amplitudes.
    Color-ordered partial amplitudes satisfy a set of well-known properties,
        \item Cyclic:\quad $$A_n^{tree}[1,2,3,\dots,n]=A_n^{tree}[2,3,\dots,n,1]$$
        \item Reflection: \quad $$A_n^{tree}[1,2,3,\dots,n]=(-1)^nA_n^{tree}[n,\dots,3,2,1]$$
        \item "photon" decoupling: \quad $$\sum_{\sigma\in \text{cyclic}}A_n^{tree}[1,\sigma(2,3,\dots,n)]=0$$
        \item KK(Kleiss-Kuijf) relation:\quad $$A_n^{tree}[1,{\alpha},n,{\beta}]=(-1)^{n_\beta}
        \sum_{\left\{\sigma\right\}_i\in OP(\left\{\alpha\right\},\left\{\beta\right\}^T)}A_n^{tree}[1,\left\{\sigma\right\}_i,n]$$
    where the OP means ordered permutaions, that is all permutations of$\left\{\alpha\right\},\left\{\beta\right\}^T$
    that matains the order of individual elements of each set.
    For example, a five point amplitude $A_n^{tree}(1,\{2,3\},5,\{4\})$, we have
    A_n^{tree}[1,2,3,5,4]=-A_n^{tree}[1,2,3,4,5]-A_n^{tree}[1,2,4,3,5]-A_n^{tree}[1,4,2,3,5]
The other five point relations can be obtained by permuting legs 2,3,4 and using cyclic and reflection properties.
This means that the six amplitudes $A_n^{tree}(1,\mathcal{P}\{2,3,4 \},5 )$ form a basis of remaining five-point partial amplitudes.
\textcolor{red}{More generally, for multiplicity n, the KK relation can be used to rewrite any color-ordered partial amplitude in terms of only $(n-2)!$
basis partial amplitudes, where two legs are fixed(usually choose 1 and n).}
\begin{frame}{A Similar Structure}
    It can be proved that tree level amplitudes can also be decomposed like 
    \mathcal{A}_n^\text{tree}=\sum_{\sigma\in S_{n-2}}\tilde{f}^{a_1a_{\sigma_1}b_1}\tilde{f}^{b_1a_{\sigma_2}b_2}\cdots\tilde{f}^{b_{n-3}a_{\sigma_{n-2}}a_n}\tilde{A}_n(1,\sigma_1,\sigma_2,\ldots,\sigma_{n-2},n)
The basis is called DDM and more convenient in parctice. It is easy to realize that the number of basis amplitudes is also \textcolor{red}{$(n-2)!$} with fiexed particle labels 1 and n.
    \begin{Large}
        \textcolor{red}{How can we realize the existence of this basis?}
    \end{Large}
We just need to notice the contribution from ladder diagram
\begin{figure}[htb]
    \centering
    \includegraphics[width=1\linewidth]{1.png}
\end{figure}
And any (three vertex) diagram, by using the Jacobbi identity like 
\begin{figure}[htb]
    \centering
    \includegraphics[width=1\linewidth]{2.png}
\end{figure}
can be transformed to the ladder diagram. It has been proved that $\textcolor{red}{\tilde{A}_n(\dots)}$ here is identical to $\textcolor{red}{A_n^{tree}[\dots]}$ in the trace basis.
\begin{frame}{Color-Kinematics Duality }
The Color-Kinematics Duality here is not the complete version, but we can catch some points.
At four points we have
    A_4^{\mathrm{tree}}(1,2,3,4)+    A_4^{\mathrm{tree}}(1,3,2,4)+    A_4^{\mathrm{tree}}(1,4,2,3)=0.
%The decoupling identity does not rely on the specific polariazation and space-time, so the hold of this equation is 
%entirely due to the amplitudes' dependence on Mandelstam variables.
We recognize that the only nontrival way the equation holds accoring to $s+t+u=0$ 
    &A_4^{\mathrm{tree}}(1,2,3,4)+    A_4^{\mathrm{tree}}(1,3,2,4)+    A_4^{\mathrm{tree}}(1,4,2,3)\\
\quad&= (s+t+u)\chi=0
Considering that $A_4^{\mathrm{tree}}(1,2,3,4)$ treats $s$ and $t$ the same, and similar to the other two, we make the identification
    A_4^{\mathrm{tree}}(1,2,3,4)=u\chi,\quad   A_4^{\mathrm{tree}}(1,3,2,4)=t\chi,\quad    A_4^{\mathrm{tree}}(1,4,2,3)=s\chi
    We obtain
        tA_4^{\mathrm{tree}}(1,2,3,4)=uA_4^{\mathrm{tree}}(1,3,4,2),\\
        sA_4^{\mathrm{tree}}(1,2,3,4)=uA_4^{\mathrm{tree}}(1,4,2,3),\\
        tA_4^{\mathrm{tree}}(1,2,3,4)=sA_4^{\mathrm{tree}}(1,3,4,2).\\
    And in order to obtain the knematic analog of Jacobbi identity, it is convenient to express the amplitudes in terms of poles
    &A_4^{\mathrm{tree}}(1,2,3,4)\equiv\frac{n_s}{s}+\frac{n_t}{t},\\
    &A_4^{\mathrm{tree}}(1,3,4,2)\equiv-\frac{n_u}{u}-\frac{n_s}{s},\\
    &A_4^{\mathrm{tree}}(1,4,2,3)\equiv-\frac{n_t}{t}+\frac{n_u}{u}.
the relative sign here is just a convention.
    Combining the two relation above gives the desired identity
        \alert{n_u=n_s-n_t}
    this is exactly the same form of Jacobbi identity for the color factors.
    The full amplitude can be written like
    \mathcal{A}_4^{\mathrm{tree}}=g^2\left(\frac{n_sc_s}{s}+\frac{n_uc_u}{u}+\frac{n_tc_t}{t}\right)
    For the five point case, an example is 
    \begin{figure}[htb]
        \centering
        \includegraphics[width=1\linewidth]{FivePtTwist2.eps}
    \end{figure}
    we have the corresponding color factor Jacobbi identities like
        c_3=c_5-c_8
    so we need to have the knematic analog
        n_3=n_5-n_8
    The explict forms of all these factors can be found in the original paper \textbf{New relations for gauge theory amplituds, PRD 78, 085011}
    Full amplitudes of 5 points are
    \begin{eqnarray*}
        \mathcal {A}^\mathrm{tree}_5& = & 
        g^3\Biggl( {n_1 c_1\over s_{12}s_{45}}+{n_2 c_2\over s_{23}s_{51}}
        +{n_3 c_3 \over s_{34}s_{12}}+{n_4 c_4\over s_{45}s_{23}}
        +{n_5 c_5\over s_{51}s_{34}} +{n_{6} c_6\over s_{14}s_{25}}  \\
        &&\null \hskip .3 cm 
        + {n_7 c_7\over s_{32}s_{14}}+{n_{8} c_8\over s_{25}s_{43}}
        +{n_{9} c_9\over s_{13}s_{25}}+{n_{10} c_{10}\over s_{42}s_{13}}
        +{n_{11} c_{11}\over s_{51}s_{42}}+ {n_{12} c_{12}\over s_{12}s_{35}}  \\
        &&\null \hskip .3 cm 
        +{n_{13} c_{13}\over s_{35}s_{24}} 
        +{n_{14} c_{14}\over s_{14}s_{35}}
        +{n_{15} c_{15}\over s_{13}s_{45}}\Biggr)\,,
        \end{eqnarray*}
    This relation had been proved upto 8 points at the time and I think it has been improved to arbitrary points.  

@@

    To discribe the n-punctured sphere more properly, we can introduce the Riemann sphere as
    \begin{equation*}
        \mathbb{CP}^1\cong \mathcal{S}^2\cong \mathbb{C}\cup\{\infty\}
    \end{equation*}
    and n-punctured Riemann sphere can be discribed by $SL(2,\mathbb{C})$ affine coordinates ${\sigma_1,\sigma_2,\ldots,\sigma_n}$, that is to say we have a equvilance relation
    \begin{align*}
        \{\sigma_1,\sigma_2,\ldots,\sigma_n\}\sim\{\psi(\sigma_1),\psi(\sigma_2),\ldots,\psi(\sigma_n)\},\\\psi(\sigma):=\frac{\alpha\sigma+\beta}{\gamma\sigma+\delta},\quad\alpha,\beta,\gamma,\delta\in\mathbb{C},\alpha\delta-\beta\gamma=1
    \end{align*}
    because of the redundancy of $\mathrm{SL}(2,\mathbb{C})$, only $n-3$ of them are independent.
\end{frame}
\begin{frame}
    From this map, we can easily obtain the main ingredients of this report \\

    \begin{block}{\textcolor{red}{Scattering equations}}
        \begin{equation*}
            \sum_{b\neq a } \frac{s_{ab}}{\sigma_a-\sigma_{b}}=0,\qquad a\in \{1,\dots,n\}
        \end{equation*}
    \end{block}
    It has been proved that the number of solutions in any dimension is $\alert{(n-3)!}$, and only \alert{$n-3$} of the equtions are independent, so we can rewrite the scattering equations as following 
    \begin{equation*}
        \sum_{b\neq a } \frac{s_{ab}}{\sigma_a-\sigma_{b}}=0,\quad a\in \{4,5,\dots,n\}\quad and\quad  \sigma_1\rightarrow\infty,\sigma_2=0,\sigma_3=1
    \end{equation*}
\end{frame}
\iffalse
\begin{frame}{KLT Relation}
    So-called KLT relation, in the language of field theory, refers to the decomposition of \alert{gravity amplitudes} to \alert{two gauge theory amplitues}. 
    \begin{table}[]
        \resizebox{\textwidth}{!}{
        \begin{tabular}{|l|l|l|l|l|}
        \hline
         \(\mathcal{N}\) & Factors & Supergravity   \\ \hline
         8 &   \(\mathcal{N}=4SYM\otimes \mathcal{N}=4SYM\)      &   pure \(\mathcal{N}=8 \)SG             \\ \hline
         6 &   \(\mathcal{N}=4SYM\otimes \mathcal{N}=2SYM\)      &   pure \(\mathcal{N}=6 \)SG             \\ \hline
         5 &   \(\mathcal{N}=4SYM\otimes \mathcal{N}=1SYM\)      &   pure \(\mathcal{N}=5 \)SG             \\ \hline
         4 &   \(\mathcal{N}=4SYM\otimes (\mathcal{N}=0YM+n_\nu scalars)\)      &    \(\mathcal{N}=4 \)SG,\(n_\nu\)vector multiplets             \\ \hline
         4 &   \(\mathcal{N}=2SYM\otimes \mathcal{N}=2SYM\)      &    \(\mathcal{N}=4 \)SG,2 vector multiplets            \\ \hline
         3 &   \(\mathcal{N}=2SYM\otimes \mathcal{N}=1SYM\)      &    \(\mathcal{N}=3 \)SG,1 vector multiplet           \\ \hline
         2 &   \(\mathcal{N}=2SYM\otimes (\mathcal{N}=0YM+n_\nu scalars)\)      &    \(\mathcal{N}=2 \)SG,\(n_\nu\) multiplets+1 vector multiplets            \\ \hline
         2 &   \(\mathcal{N}=1SYM\otimes \mathcal{N}=1SYM\)       &    \(\mathcal{N}=2 \)SG ,1 hypermultiplet               \\ \hline
         1 &   \(\mathcal{N}=1SYM\otimes (\mathcal{N}=0YM+n_\nu scalars)\)      &     \(\mathcal{N}=1 \)SG,  \(n_\nu\) vector and 1 chiral multiplet           \\ \hline
        \end{tabular}
        }
        \end{table}
\end{frame}
\fi
\begin{frame}{KLT Orthogonality}
    $\bullet$ KLT orthogonality is a striking property of the solutions to scattering equations.
    \begin{block}{Proposition 1}
        \begin{equation*}
            \frac{(i,j)}{(i,i)^{\frac12}(j,j)^{\frac12}}=\delta_{ij}
        \end{equation*}
    \end{block}

@@

    It is worth to computed the measure explicitly.Aftering "gauge fixing" the $SL(2,\mathbb{C})$ redundancy, one finds 

@@

\end{frame}
\begin{frame}
    Likewise the decomposition in the first section, it is more usually to write the amplitudes in terms of colore basis
    \begin{equation*}
        \boxed{\mathbf{c}_\alpha\equiv\sum_{\mathsf{c}_1,...,\mathsf{c}_{n-3}}f_{\mathsf{a}_1\mathsf{a}_{\alpha(2)}\mathsf{c}_1}\cdots f_{\mathsf{c}_{n-3}\mathsf{a}_{\alpha(n-1)}\mathsf{a}_n}}
    \end{equation*}
    where $\alpha \in S_{n-2}$. The amplitude is 
    \begin{equation*}
        \mathcal{M}_n^{(0)}=\sum_{\alpha,\beta\in S_{n-2}}\mathbf{c_\alpha}\tilde{\mathbf{c_\beta}}m_{n}^{(0)}(\alpha|\beta)
    \end{equation*}
\end{frame}
\begin{frame}
    \frametitle{Examples}
    \begin{itemize}
        \item The simplest example is the 3 point case
        \begin{equation*}
            \mathcal{M}_3^{(0)}(1^{aa^\prime,bb^\prime,cc^\prime})=(\sigma_{12}\sigma_{23}\sigma_{31})^2\frac{f_{abc}f_{a^\prime b^\prime c^\prime}}{(\sigma_{12}\sigma_{23}\sigma_{31})^2}=f_{abc}f_{a^\prime b^\prime c^\prime}
        \end{equation*}
        It actually gives the correct answer.
        \item The 4 point case is a little complex. Solving the scattering equations with $\sigma_1=0,\sigma_2=1,\sigma_3=\infty$ gives $\sigma_4=-s_{23}/s_{12}$. Define
        $s_{12}=s$, $s_{23}=t$, $s_{13}=u$, the color factors are 
        \begin{equation*}
            \mathbf{c_s}=\sum_bf_{a_1a_2b}f_{ba_3a_4},\mathbf{c_t}=\sum_bf_{a_1a_4b}f_{ba_3a_2},\mathbf{c_u}=\sum_bf_{a_1a_3b}f_{ba_2a_4}
        \end{equation*}
        Denoting the ordering $(1324)$ as $P$ and comuputing $\det{'}\Phi=\frac{s^2}{t}/(\sigma_{12}\sigma_{23}^2\sigma_{31}\sigma_{34}\sigma_{42})$, one gets
    \end{itemize}
\end{frame}
\begin{frame}
    \begin{align*}
        \!\!\!\!\mathcal{M}_4^{(0)}&=\mathbf{c_s}\tilde{\mathbf{c_s}}m_4^{(0)}(I;I)+\mathbf{c_s}\tilde{\mathbf{c_u}}m_4^{(0)}(I;P)+\mathbf{c_u}\tilde{\mathbf{c_s}}m_4^{(0)}(P;I)+\mathbf{c_u}\tilde{\mathbf{c_u}}m_4^{(0)}(P;P)\\
        &=\mathbf{c_s}\tilde{\mathbf{c_s}}\frac{u}{st}+(\mathbf{c_s}\tilde{\mathbf{c_u}}+\mathbf{c_u}\tilde{\mathbf{c_s}})\frac{1}{t}+\mathbf{c_u}\tilde{\mathbf{c_u}}\frac{s}{ut}\\
        &=-\frac{\mathbf{c_s}\tilde{\mathbf{c_s}}}{s}-\frac{\mathbf{c_t}\tilde{\mathbf{c_t}}}{t}-\frac{\mathbf{c_u}\tilde{\mathbf{c_u}}}{u}
    \end{align*}
    \quad \quad as expected for a color-dressed cubic theory.
    \begin{itemize}
        \item For the five point, I just give the results of some double partial amplitudes.
        Denoting the orderings as $I=P_0$, $(13245)=P_1$, $(12435)=P_2$, $(14325)=P_3$, $(13425)=P_4$, $(14235)=P_5$
        \begin{equation*}
            \begin{aligned}&m_5^{(0)}(I|I)=\frac{1}{s_{12}s_{34}}+\frac{1}{s_{23}s_{45}}+\frac{1}{s_{34}s_{51}}+\frac{1}{s_{45}s_{12}}+\frac{1}{s_{51}s_{23}},\\&m_5^{(0)}(I|P_1)=-\frac{1}{s_{23}}\left(\frac{1}{s_{45}}+\frac{1}{s_{12}}\right),\quad
                m_5^{(0)}(I|P_2)=-\frac{1}{s_{34}}\left(\frac{1}{s_{51}}+\frac{1}{s_{12}}\right).\end{aligned}
        \end{equation*}
    \end{itemize}
\end{frame}
\begin{frame}
    \begin{align*}
        &m_5^{(0)}(I|P_3)=-\frac{1}{s_{51}}\left(\frac{1}{s_{23}}+\frac{1}{s_{34}}\right),\quad  m_5^{(0)}(I|P_4)=-\frac{1}{s_{34}s_{51}},\\
        &m_5^{(0)}(I|P_5)=0
    \end{align*}
    From there examples, it is easy to see that when both permutations in $m_n^{(0)}(\alpha|\beta)$ are the same, then the answer is a sum over all color-orded
    trivalent diagrams; When the two permutations are different, it gives a subset of terms of $m_n^{(0)}(\alpha|\alpha)$. 
    \\ \hspace*{\fill}\\
    More explicitly,
